Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-06 paper/section-general-framework.tex
Incorporate the well-indexed context rules into the figure

Well-typed programs are defined with respect to well-indexed typing
contexts, which are in turn defined with respect to an index
context. Well-indexed typing contexts with respect to an index context
$\Delta$ are sequences of variable/type pairs with no repeated
variable names such that each type is well-indexed with respect to
$\Delta$. Formally, well-indexed typing contexts are defined by the
following two rules:
\begin{mathpar}
  \inferrule*
  { }
  {\Delta \vdash \epsilon \isCtxt}

  \inferrule*
  {\Delta \vdash \Gamma \isCtxt \\ \Delta \vdash A \isType \\ x \not\in \Gamma}
  {\Delta \vdash \Gamma, x : A \isCtxt}
\end{mathpar}
Application of simultaneous substitutions extends to typing contexts
by applying the simultaneous substitution to each type.

The typing rules for our system define the well-typed programs with
respect to an index context $\Delta$ and a type context $\Delta \vdash
\Gamma \isCtxt$. The judgment $\Delta; \Gamma \vdash M : A$ is defined
in \autoref{fig:programs}. The equational theory on types is
incorporated into the type system via the rule \TirName{TyEq}, which
allows for a program that is judged to have type $A$ to also have any
other equal type $B$.
\begin{figure*}[t]
  \centering
  {\tiny
  \begin{mathpar}
    \inferrule* [right=Var]
    {\Delta \vdash \Gamma \isCtxt \\ x : A \in \Gamma}
    {\Delta; \Gamma \vdash x : A}

@@

  \caption{Well-typed Programs}
  \label{fig:programs}
\end{figure*}

>>>>

Well-typed programs are defined with respect to well-indexed typing
contexts, which are in turn defined with respect to an index
context. Well-indexed typing contexts $\Delta \vdash \Gamma \isCtxt$
with respect to an index context $\Delta$ are sequences of
variable/type pairs with no repeated variable names such that each
type is well-indexed with respect to $\Delta$. Formally, well-indexed
typing contexts are defined by the two rules in
\autoref{fig:programs}.  Application of simultaneous substitutions
extends to typing contexts by applying the simultaneous substitution
to each type.

The typing rules for our system define the well-typed programs with
respect to an index context $\Delta$ and a type context $\Delta \vdash
\Gamma \isCtxt$. The judgment $\Delta; \Gamma \vdash M : A$ is defined
in \autoref{fig:programs}. The equational theory on types is
incorporated into the type system via the rule \TirName{TyEq}, which
allows for a program that is judged to have type $A$ to also have any
other equal type $B$.
\begin{figure*}[t]
  \centering
  {\tiny
    \begin{mathpar}
      \inferrule*
      { }
      {\Delta \vdash \epsilon \isCtxt}

      \inferrule*
      {\Delta \vdash \Gamma \isCtxt \\ \Delta \vdash A \isType \\ x \not\in \Gamma}
      {\Delta \vdash \Gamma, x : A \isCtxt}

      \inferrule* [right=Var]
      {\Delta \vdash \Gamma \isCtxt \\ x : A \in \Gamma}
      {\Delta; \Gamma \vdash x : A}

@@

  \caption{Well-indexed Contexts and Well-typed Programs}
  \label{fig:programs}
\end{figure*}
